---
title: "Analysis: Codes By Facility"
output: 
  html_document:
    theme: flatly
    toc: FALSE
---
<br>

---

## Introduction
This markdown imports the answer key for each facility and creates a visualization of the answers.

* Data Wrangling for this analysis
* Stacked Barplot for All Questions


---

## Required Packages
The following R packages are required for this script:

* here: for path setting
* tidyverse: for all packages in the Tidyverse (ggplot2, dyplr, tidyr, readr, purr, tibble, stringr, forcats)
* ggpattern: for adding a pattern to the grid
* extrafont: for changing ggplot fonts

```{r libraries, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)

#load required packages
library(here)
library(tidyverse)
library(ggpattern)
library(extrafont)

#global environment options
# formatting for script to avoid scientific notation output
options(scipen=999)

#set ggplot theme to classic
ggplot2::theme_set(theme_classic())

#center plot titles
theme_update(plot.title = element_text(hjust = 0.5))

#load fonts
loadfonts(device = "win")
```

---

## Load Data
Load the data in the `raw_data`` folder.
```{r load data}
#define file path
data_location <- here::here("data", "raw_data", "codekey.csv")

#load data
key <- read.csv(data_location)
```

---

## Convert to Long Format
```{r long format}
key_long <- key %>%
              tidyr::gather(Emergency, Code, `Fire`:`Hostage.Situation`, factor_key = TRUE)

#change labels
levels(key_long$Emergency) <- c("Fire", "Cardiac Arrest", "Pediatric Emergency", "Bomb Threat", "Violence", "Active Shooter", "Infant Abduction",
                                "Mass Casualty", "Internal Disaster", "Hazardous Materials", "Missing Adult", "Severe Weather", "Missing Child",
                                "Hostage Situation")

#add column for code type
key_long$Type <- key_long$Code

#add column for color codes
key_long$ColorCode <- key_long$Code

#Replace any colors with the word "color"
key_long$Type[key_long$Type == "Red"] <- "Color Code"
key_long$Type[key_long$Type == "Blue"] <- "Color Code"
key_long$Type[key_long$Type == "Gray"] <- "Color Code"
key_long$Type[key_long$Type == "Black"] <- "Color Code"
key_long$Type[key_long$Type == "Silver"] <- "Color Code"
key_long$Type[key_long$Type == "Pink"] <- "Color Code"
key_long$Type[key_long$Type == "Orange"] <- "Color Code"
key_long$Type[key_long$Type == "Gold"] <- "Color Code"
key_long$Type[key_long$Type == "Green"] <- "Color Code"

#fix type category
key_long$Type[key_long$Type == "Code Strong"] <- "Other"
key_long$Type[key_long$Type == "Security Stat"] <- "Other"
key_long$Type[key_long$Type == "Code Triage"] <- "Other"
key_long$Type[key_long$Type == "Code Triage A"] <- "Other"
key_long$Type[key_long$Type == "Code Triage B"] <- "Other"
key_long$Type[key_long$Type == "Code [Facility]"] <- "Other"
key_long$Type[key_long$Type == "Code E"] <- "Other"

#Replace any "other" codes in code column
key_long$ColorCode[key_long$ColorCode == "None Identified"] <- "Not a Color Code"
key_long$ColorCode[key_long$ColorCode == "Code Strong"] <- "Not a Color Code"
key_long$ColorCode[key_long$ColorCode == "Security Stat"] <- "Not a Color Code"
key_long$ColorCode[key_long$ColorCode == "Code Triage"] <- "Not a Color Code"
key_long$ColorCode[key_long$ColorCode == "Code Triage A"] <- "Not a Color Code"
key_long$ColorCode[key_long$ColorCode == "Code Triage B"] <- "Not a Color Code"
key_long$ColorCode[key_long$ColorCode == "Code [Facility]"] <- "Not a Color Code"
key_long$ColorCode[key_long$ColorCode == "Code E"] <- "Not a Color Code"
key_long$ColorCode[key_long$ColorCode == "Plain Language"] <- "Not a Color Code"
```

---

## Plot Different Codes for Each Emergency
Option 1: Color Codes and Label any "Other" or "Plain Language" codes
```{r codes by emergency plot}
#unique values of codes
# "Red"             "Blue"            "None Identified" "Gray"            "Black"           "Code Strong"     "Security Stat"   "Silver"         
# "Pink"            "Code Triage"     "Code Triage A"   "Code Triage B"   "Code [Facility]" "Orange"          "Gold"            "Code E"         
# "Green"           "Plain Language" 

codes_emergency_plot <- key_long %>%
                              dplyr::group_by(Emergency, Code, Type, ColorCode) %>%
                              dplyr::count(Code) %>%
                              ggplot2::ggplot(aes(x = Emergency,
                                                  y = n)) +
                              ggplot2::geom_bar(aes(fill = ColorCode),
                                                position = "fill",
                                                stat = "identity",
                                                color = "black") +
                              ggplot2::scale_y_continuous(labels = scales::percent,
                                                      expand = c(0,0)) +
                              ggplot2::scale_fill_manual(values = c("Red" = "firebrick1",
                                                                 "Blue" = "dodgerblue",
                                                                 "Not a Color Code" = "white",
                                                                 "Gray" = "darkgray",
                                                                 "Black" = "black",
                                                                 "Silver" = "grey90",
                                                                 "Pink" = "hotpink",
                                                                 "Orange" = "darkorange",
                                                                 "Gold" = "gold",
                                                                 "Green" = "springgreen3")) +
                              ggplot2::labs(x = " ",
                                            y = "Percent of Facilities") +
                              ggplot2::theme(text = element_text(family = "sans"),
                                             axis.text = element_text(color = "black"),
                                             axis.text.x = element_text(angle = 90,
                                                                        vjust = 0.5,
                                                                        hjust = 1)) +
                              ggplot2::annotate(geom = "text",
                                                x = 5,
                                                y = 0.1,
                                                angle = 90,
                                                label = stringr::str_wrap("Code Strong", 3),
                                                lineheight = 0.65) +
                              ggplot2::annotate(geom = "text",
                                                x = 5,
                                                y = 0.4,
                                                angle = 90,
                                                label = "Security Stat") +
                              ggplot2::annotate(geom = "text",
                                                x = 8,
                                                y = 0.3,
                                                angle = 90,
                                                label = "Code Triage") +
                              ggplot2::annotate(geom = "text",
                                                x = 8,
                                                y = 0.8,
                                                angle = 90,
                                                label = "Code Triage A") +
                              ggplot2::annotate(geom = "text",
                                                x = 9,
                                                y = 0.4,
                                                angle = 90,
                                                label = "Code Triage B") +
                              ggplot2::annotate(geom = "text",
                                                x = 9,
                                                y = 0.7,
                                                angle = 90,
                                                label = stringr::str_wrap("Code [Facility]", 3),
                                                lineheight = 0.7) +
                              ggplot2::annotate(geom = "text",
                                                x = 11,
                                                y = 0.2,
                                                angle = 90,
                                                label = "Code E") +
                              ggplot2::annotate(geom = "text",
                                                x = 12,
                                                y = 0.2,
                                                angle = 90,
                                                label = "Plain Language") +
                              ggplot2::guides(fill = guide_legend(ncol = 2))
  
codes_emergency_plot

#patterns that work: none, weave, stripe, circle, crosshatch
```

<br>

Option 2: Pattern by Code Type
```{r codes by emergency plot 2}
#unique values of codes
# "Red"             "Blue"            "None Identified" "Gray"            "Black"           "Code Strong"     "Security Stat"   "Silver"         
# "Pink"            "Code Triage"     "Code Triage A"   "Code Triage B"   "Code [Facility]" "Orange"          "Gold"            "Code E"         
# "Green"           "Plain Language" 

#order emergencies
emergency_order <- c("Active Shooter", "Bomb Threat", "Cardiac Arrest", "Fire", "Hazardous Materials", "Hostage Situation", "Infant Abduction",
                     "Internal Disaster", "Mass Casualty", "Missing Adult", "Missing Child", "Pediatric Emergency", "Severe Weather", "Violence")


codes_emergency_plot2 <- key_long %>%
                              dplyr::group_by(Emergency, Code, Type, ColorCode) %>%
                              dplyr::count(Code) %>%
                              ggplot2::ggplot(aes(x = factor(Emergency, level = emergency_order),
                                                  y = n,
                                                  fill = ColorCode,
                                                  pattern = Type)) +
                              ggpattern::geom_bar_pattern(position = "fill",
                                                stat = "identity",
                                                color = "black",
                                                pattern_fill = "black",
                                                pattern_angle = 45,
                                                pattern_density = 0.1,
                                                pattern_spacing = 0.025,
                                                pattern_key_scale_factor = 0.6) +
                              ggpattern::scale_pattern_manual(values = c("Color Code" = "none",
                                                                         "None Identified" = "stripe",
                                                                         "Other" = "circle",
                                                                         "Plain Language" = "crosshatch")) +
                              ggplot2::scale_y_continuous(labels = scales::percent,
                                                      expand = c(0,0)) +
                              ggplot2::scale_fill_manual(values = c("Pink" = "#EE4C97FF",
                                                                    "Red" = "#BC3C29FF",
                                                                    "Orange" = "#E18727FF",
                                                                    "Gold" = "#FFDC91FF",
                                                                    "Green" = "#20854EFF",
                                                                    "Blue" = "#6F99ADFF",
                                                                    "Gray" = "gray47",
                                                                    "Silver" = "grey84",
                                                                    "Black" = "black",
                                                                    "Not a Color Code" = "white")) +
                              ggplot2::labs(x = " ",
                                            y = "Percent of Facilities",
                                            pattern = "Code Type",
                                            fill = "Color Code") +
                              ggplot2::theme(text = element_text(family = "Palatino Linotype"),
                                             axis.text = element_text(color = "black"),
                                             axis.text.x = element_text(angle = 90,
                                                                        vjust = 0.5,
                                                                        hjust = 1)) +
                              ggplot2::guides(pattern = guide_legend(override.aes = list(fill = "white"),
                                                                     ncol = 2),
                                              fill = guide_legend(override.aes = list(pattern = "none"),
                                                                  ncol = 2))

codes_emergency_plot2

codes_emergency_file = here("results", "codes", "emergency_codes.png")
ggsave(filename = codes_emergency_file, 
       plot = codes_emergency_plot2, dpi = 300)
```


