---
title: "Analysis: Exploratory Data Analysis"
output: 
  html_document:
    theme: flatly
    toc: FALSE
---
<br>

---

## Introduction
This markdown imports the processed data and conducts the exploratory data analysis. Follow the processing markdowns in the `processing_code` folder to generate the processed data.

<br>

This analysis examines the predictors of performance on the code survey. In terms of the dataset, the three (potential) outcomes of interest are Overall Grade (`GradeOverall`), Code Type Grade (`GradeType`), and Code Answer Grade (`CodeScore`).

<br>

It also creates the summary table in the manuscript.

---

## Required Packages
The following R packages are required for this script:

* here: for path setting
* tidyverse: for all packages in the Tidyverse (ggplot2, dyplr, tidyr, readr, purr, tibble, stringr, forcats)
* skimr: for data summarization
* summarytools: for overall dataframe summary
* car: for creating QQ plots
* gtsummary: for creating tables for summary statistics / other numerical outputs
* flextable: for outputting tables in word
* extrafont: for changing the font of ggplots

```{r libraries, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)

#load required packages
library(here) #to set paths
library(tidyverse) #for data processing
library(skimr) #for data summarization
library(summarytools) #for overall dataframe summary
library(car) #for creating QQ plots
library(gtsummary) #for creating tables
library(flextable) #for outputting to word
library(extrafont) #for changing ggplot fonts


#global environment options
# formatting for script to avoid scientific notation output
options(scipen=999)

#set ggplot theme to classic
ggplot2::theme_set(theme_classic())

#center plot titles
ggplot2::theme_update(plot.title = element_text(hjust = 0.5))

#set gtsummary theme
gtsummary::theme_gtsummary_compact()

#load fonts
loadfonts(device = "win")

```

---

## Load Processed Data
Load the data generated from the markdowns in the `processing_code` folder.
```{r load data}
#define file path
data_location <- here::here("data", "processed_data", "full_processed.rds")

#load data
EDAdata <- readRDS(data_location)
```

---

## Data Overview
To better understand the data, let's use `summarytools` to better visualize the data.
```{r data overview}
summarytools::dfSummary(EDAdata)

skimr::skim(EDAdata)
```
Looking at the output of `summarytools::dfsummary()`

* There are 304 completed survey responses
* `GradeOverall` ranges from 0.1 to 1, with a mean of 0.5
* `GradeType` ranges from 0.1 to 1, with a mean of 0.6
* `CodeScore` ranges from 0 to 1, with a mean of 0.4
* There still appears to be a preference to keep color codes

Let's dive a little deeper into each variable.

---

## Outcome of Interest: Overall Performance
The first potential outcome of interest is the overall performance across all survey questions.
```{r overall performance}
#summary statistics
base::summary(EDAdata$`GradeOverall`)

#density plot
ggplot2::ggplot(data = EDAdata, aes(x = `GradeOverall`)) +
  geom_density()

#normal boxplot
ggplot2::ggplot(data = EDAdata, aes(y = `GradeOverall`)) +
  geom_boxplot()

##QQ plot
car::qqPlot(EDAdata$`GradeOverall`)
```

These outputs show the overall performance is relatively normally distributed. There really don't seem to be any outliers, and it does not appear to require any transformation.

---

## Outcome of Interest: Code Type Performance
The next potential outcome of interest is the performance across survey questions that asked about the type of code for each hazard.
```{r type performance}
#summary statistics
base::summary(EDAdata$`GradeType`)

#density plot
ggplot2::ggplot(data = EDAdata, aes(x = `GradeType`)) +
  geom_density()

#normal boxplot
ggplot2::ggplot(data = EDAdata, aes(y = `GradeType`)) +
  geom_boxplot()

##QQ plot
car::qqPlot(EDAdata$`GradeType`)
```

These outputs show the overall performance is relatively normally distributed. There are a few potential outliers, and the distribution is just slightly skewed to the right.

---

## Outcome of Interest: Code Answer Performance
The last potential outcome of interest is the performance across survey questions that asked participants to identify the specific code for each hazard.
```{r answer performance}
#summary statistics
base::summary(EDAdata$`CodeScore`)

#density plot
ggplot2::ggplot(data = EDAdata, aes(x = `CodeScore`)) +
  geom_density()

#normal boxplot
ggplot2::ggplot(data = EDAdata, aes(y = `CodeScore`)) +
  geom_boxplot()

##QQ plot
car::qqPlot(EDAdata$`CodeScore`)
```

These outputs show the overall performance is relatively normally distributed. There really don't seem to be any outliers, and it does not appear to require any transformation.

---

## Compare Outcomes of Interest
Before moving on, let's create a plot to compare the distribution of the three outcomes.
```{r outcome comparison plot}
#convert to long format in order to be able to plot all three outcomes with the same variable
data_long <- tidyr::gather(EDAdata, GradeCat, score, `GradeOverall`:`CodeScore`, factor_key = TRUE)

#change labels
levels(data_long$GradeCat) <- c("Overall Score", "Code Type Score", "Code Answer Score")

#now usual ggplot2 density plot
#now usual ggplot2 density plot
outcomes_density <- ggplot2::ggplot(data = data_long, aes(x = score, color = GradeCat, fill = GradeCat)) +
                          geom_density(alpha = 0.4) +
                          facet_wrap(~ GradeCat) +
                          scale_x_continuous(labels = scales::percent) +
                          labs(x = "Percent of Correct Responses",
                               y = "Density") +
                          theme(legend.position="none")

outcomes_density

#save file
outcomes_density_fig_file = here("results", "eda", "outcomes_density.png")
ggsave(filename = outcomes_density_fig_file, plot = outcomes_density)
```
Looking at the distributions, they're all relatively similar. I think it makes the most sense to move forward with grade for the code answer.

Therefore, let's make a distribution plot of code answer accuracy
```{r code answer distribution}
#find mean of code answer
mean(EDAdata$`CodeScore`)

#find standard deviation of code answer
sd(EDAdata$`CodeScore`)

# Histogram
codegrade_plot <- EDAdata %>% 
                    ggplot(aes(x = CodeScorePct)) +
                    geom_histogram(aes(y = ..count..), 
                                   binwidth = 10, 
                                   alpha = 0.85,
                                   fill = "#6F99ADFF",
                                   color = "#4A6673") +
                    geom_vline(xintercept = mean(EDAdata$CodeScorePct, na.rm=T), 
                               linetype = 2) + 
                    annotate("text", x = mean(EDAdata$CodeScore, na.rm=T), 
                                     y = 0, 
                                     label = "Mean = 44.37%", 
                                     vjust = -30, 
                                     hjust = -2.6,
                             family = "Palatino Linotype") +
                    scale_x_continuous(breaks = seq(0, 100, by = 10)) + 
                    coord_cartesian(xlim = c(0,100)) +
                    scale_y_continuous(expand = c(0,0),
                                       limits = c(0, 100)) +
                    labs(y = "Number of Participants", 
                         x = "Code Identification Accuracy (%)") +
                    theme(axis.text = element_text(color = "black"),
                          text = element_text(family = "Palatino Linotype"))

codegrade_plot

#save plot
code_grade_plot = here::here("results", "eda", "code_grade_plot.png")
ggsave(filename = code_grade_plot, 
       plot = codegrade_plot,
       dpi = 300)
```

---


---

## Tables
Make the summary tables for the manuscript. 

### Participant Demographics Table

Variables to include:

* FacilityLabel
* PositionType
* ShiftType,
* FacilityYears,
* HealthcareYears
* FacilitiesNumber

```{r demographics table}
#create table
demographics_table <- EDAdata %>%
                        dplyr::select(c(FacilityLabel,
                                        PositionType,
                                        ShiftType,
                                        FacilityYears,
                                        HealthcareYears,
                                        FacilitiesNumber)) %>%
                        gtsummary::tbl_summary(by = FacilityLabel,
                                               statistic = list(all_continuous() ~ "{mean} ({sd})",
                                                                all_categorical() ~ "{n} ({p}%)"),
                                               digits = all_continuous() ~ 2,
                                               type = all_dichotomous() ~ "categorical") %>%
                        gtsummary::add_overall(last = TRUE) %>%
                        gtsummary::modify_header(label ~ " ") %>%
                        gtsummary::modify_spanning_header(c("stat_1", "stat_2", "stat_3", "stat_4", "stat_5") ~ "**Facility**") %>%
                        gtsummary::bold_labels() %>%
                        gtsummary::modify_caption("Table 1. Survey participant demographic characteristics")

demographics_table

#save as RDS
demographics_file = here::here("results", "demographics_table.Rds")

saveRDS(demographics_table, file = demographics_file)

```

---

### Experience with Codes Table

Variables to include:

* Facility-Label
* CodeProcedures
* Codeconfusion
* Facilitiesdifferentcodes
* CodePreference
* Codeexceptions
* TrainingOrientation
* TrainingExercises
* TrainingYearly
* Traininglasttime

```{r code experience table}
#create table
experience_table <- EDAdata %>%
                        dplyr::select(c(FacilityLabel,
                                        CodeProcedures,
                                        Codeconfusion,
                                        Facilitiesdifferentcodes,
                                        CodePreference,
                                        Codeexceptions,
                                        TrainingOrientation,
                                        TrainingExercises,
                                        TrainingYearly,
                                        Traininglasttime)) %>%
                        gtsummary::tbl_summary(by = FacilityLabel,
                                               statistic = list(all_continuous() ~ "{mean} ({sd})",
                                                                all_categorical() ~ "{n} ({p}%)"),
                                               digits = all_continuous() ~ 2,
                                               type = all_dichotomous() ~ "categorical") %>%
                        gtsummary::add_overall(last = TRUE) %>%
                        gtsummary::modify_header(label ~ " ") %>%
                        gtsummary::modify_spanning_header(c("stat_1", "stat_2", "stat_3", "stat_4", "stat_5") ~ "**Facility**") %>%
                        gtsummary::bold_labels() %>%
                        gtsummary::modify_caption("Table 2. Survey participant experience with emergency codes")

experience_table

#save as RDS
experience_file = here::here("results", "experience_table.Rds")

saveRDS(experience_table, file = experience_file)
```


