---
title: "Analysis: Bivariate Analysis for Demographic Variables"
output: 
  html_document:
    theme: flatly
    toc: FALSE
---
<br>

---

## Introduction
This markdown imports the processed analysis data and conducts a bivaraiate analysis for the outcomes of interest: change in confidence score and code identification score.

For each variable, the following steps are taken:

* Summary statistics
* ANOVA
* ANOVA with Tukey correction
* Box Plot Visualization if significant

---

## Required Packages
The following R packages are required for this script:

* here: for path setting
* tidyverse: for all packages in the Tidyverse (ggplot2, dyplr, tidyr, readr, purr, tibble, stringr, forcats)
* rstatix: for summary stats
* agricolae: for more detailed output of Tukey HSD
* broom: for making prettier outputs of regressions
* ggpubr: for making box plots of significant variables
* gtsummary: for making summary tables

```{r libraries, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)

#load required packages
library(here)
library(tidyverse)
library(rstatix)
library(agricolae)
library(broom)
library(ggpubr)
library(gtsummary)

#global environment options
# formatting for script to avoid scientific notation output
options(scipen=999)

#set ggplot theme to classic
ggplot2::theme_set(theme_classic())

#center plot titles
ggplot2::theme_update(plot.title = element_text(hjust = 0.5))

#set gtsummary theme
gtsummary::theme_gtsummary_compact()
```

---

## Load Processed Data
Load the data generated from the markdowns in the `processing_code` folder.
```{r load data}
#define file path
data_location <- here::here("data", "processed_data", "analysis_processed.rds")

#load data
analysis_data <- readRDS(data_location)
```

---

## Code Identification Score
Each variable will be analyzed where y = `CodeScorePct` (the percent of correctly identified codes during the survey).

---

### Facility Label

1. Summary Statistics
```{r facility label summary statistics code ID}
facility_sum_stats1 <- analysis_data %>%
                          dplyr::group_by(FacilityLabel) %>%
                          rstatix::get_summary_stats(CodeScorePct, type = "mean_sd")
facility_sum_stats1
```

<br>

2. ANOVA
```{r facility label anova code ID}
facility_anova1 <- stats::aov(CodeScorePct ~ FacilityLabel, data = analysis_data)

summary(facility_anova1)
```

<br>

3. ANOVA with Tukey Correction
```{r facility label tukey code ID}
facility_tukey1 <- agricolae::HSD.test(facility_anova1, trt = "FacilityLabel")

facility_tukey1

TukeyHSD(facility_anova1, "FacilityLabel")
```

At least one mean is different among the facilities. Significant difference between B/C and D and A/E.

---

### PositionType
1. Summary Statistics
```{r position type summary statistics code ID}
position_sum_stats1 <- analysis_data %>%
                          dplyr::group_by(PositionType) %>%
                          rstatix::get_summary_stats(CodeScorePct, type = "mean_sd")
position_sum_stats1
```

<br>

2. ANOVA
```{r position type anova code ID}
position_anova1 <- stats::aov(CodeScorePct ~ PositionType, data = analysis_data)

summary(position_anova1)
```

<br>

3. ANOVA with Tukey Correction
```{r position type tukey code ID}
position_tukey1 <- agricolae::HSD.test(position_anova1, trt = "PositionType")

position_tukey1
```
There is not a significant difference in the mean code identification score by position type.

---

### ShiftType
1. Summary Statistics
```{r shift type summary statistics code ID}
shift_sum_stats1 <- analysis_data %>%
                        dplyr::group_by(ShiftType) %>%
                        rstatix::get_summary_stats(CodeScorePct, type = "mean_sd")
shift_sum_stats1
```

<br>

2. ANOVA
```{r shift type anova code ID}
shift_anova1 <- stats::aov(CodeScorePct ~ ShiftType, data = analysis_data)

summary(shift_anova1)
```

<br>

3. ANOVA with Tukey Correction
```{r shift type tukey code ID}
shift_tukey1 <- agricolae::HSD.test(shift_anova1, trt = "ShiftType")

shift_tukey1
```
There is not a significant difference in the mean code identification score by shift type.

---

### FacilityYears
1. Summary Statistics
```{r facility years summary statistics code ID}
facilityyrs_sum_stats1 <- analysis_data %>%
                            dplyr::group_by(FacilityYears) %>%
                            rstatix::get_summary_stats(CodeScorePct, type = "mean_sd")
facilityyrs_sum_stats1
```

<br>

2. ANOVA
```{r facility years anova code ID}
facilityyrs_anova1 <- stats::aov(CodeScorePct ~ FacilityYears, data = analysis_data)

summary(facilityyrs_anova1)
```

<br>

3. ANOVA with Tukey Correction
```{r facility years tukey code ID}
facilityyrs_tukey1 <- agricolae::HSD.test(facilityyrs_anova1, trt = "FacilityYears")

facilityyrs_tukey1

TukeyHSD(facilityyrs_anova1, "FacilityYears")
```

At least one group is significantly different than the others. Though it disappears after Tukey correction.

---

### HealthcareYears
1. Summary Statistics
```{r healthcare years summary statistics code ID}
healthcareyrs_sum_stats1 <- analysis_data %>%
                              dplyr::group_by(HealthcareYears) %>%
                              rstatix::get_summary_stats(CodeScorePct, type = "mean_sd")
healthcareyrs_sum_stats1
```

<br>

2. ANOVA
```{r healthcare years anova code ID}
healthcareyrs_anova1 <- stats::aov(CodeScorePct ~ HealthcareYears, data = analysis_data)

summary(healthcareyrs_anova1)
```

<br>

3. ANOVA with Tukey Correction
```{r healthcare years tukey code ID}
healthcareyrs_tukey1 <- agricolae::HSD.test(healthcareyrs_anova1, trt = "HealthcareYears")

healthcareyrs_tukey1

TukeyHSD(healthcareyrs_anova1, "HealthcareYears")
```
At least one mean is significantly different. 5-8 is different than 0-2 / 2-5 years.

---

### FacilitiesNumber
1. Summary Statistics
```{r facilities number summary statistics code ID}
numfacilities_sum_stats1 <- analysis_data %>%
                              dplyr::group_by(FacilitiesNumber) %>%
                              rstatix::get_summary_stats(CodeScorePct, type = "mean_sd")
numfacilities_sum_stats1
```

<br>

2. ANOVA
```{r facilities number anova code ID}
numfacilities_anova1 <- stats::aov(CodeScorePct ~ FacilitiesNumber, data = analysis_data)

summary(numfacilities_anova1)
```

<br>

3. ANOVA with Tukey Correction
```{r facilities number tukey code ID}
numfacilities_tukey1 <- agricolae::HSD.test(numfacilities_anova1, trt = "FacilitiesNumber")

numfacilities_tukey1
```
There is not a significant difference in the mean of score by number of facilities worked.

---

## Change in Confidence Score
Each variable will be analyzed where y = `Delta` (the change in confidence score pre/post survey).

---

### Facility Label

1. Summary Statistics
```{r facility label summary statistics conf score}
facility_sum_stats2 <- analysis_data %>%
                          dplyr::group_by(FacilityLabel) %>%
                          rstatix::get_summary_stats(Delta, type = "mean_sd")
facility_sum_stats2
```

<br>

2. ANOVA
```{r facility label anova conf score}
facility_anova2 <- stats::aov(Delta ~ FacilityLabel, data = analysis_data)

summary(facility_anova2)
```

<br>

3. ANOVA with Tukey Correction
```{r facility label tukey conf score}
facility_tukey2 <- agricolae::HSD.test(facility_anova2, trt = "FacilityLabel")

facility_tukey2
```

Facility is not significantly associated with change in confidence score.

---

### PositionType
1. Summary Statistics
```{r position type summary statistics conf score}
position_sum_stats2 <- analysis_data %>%
                          dplyr::group_by(PositionType) %>%
                          rstatix::get_summary_stats(Delta, type = "mean_sd")
position_sum_stats2
```

<br>

2. ANOVA
```{r position type anova conf score}
position_anova2 <- stats::aov(Delta ~ PositionType, data = analysis_data)

summary(position_anova2)
```

<br>

3. ANOVA with Tukey Correction
```{r position type tukey conf score}
position_tukey2 <- agricolae::HSD.test(position_anova2, trt = "PositionType")

position_tukey2
```
Position Type is not significantly associated with change in confidence score.

---

### ShiftType
1. Summary Statistics
```{r shift type summary statistics conf score}
shift_sum_stats2 <- analysis_data %>%
                        dplyr::group_by(ShiftType) %>%
                        rstatix::get_summary_stats(Delta, type = "mean_sd")
shift_sum_stats2
```

<br>

2. ANOVA
```{r shift type anova conf score}
shift_anova2 <- stats::aov(Delta ~ ShiftType, data = analysis_data)

summary(shift_anova2)
```

<br>

3. ANOVA with Tukey Correction
```{r shift type tukey conf score}
shift_tukey2 <- agricolae::HSD.test(shift_anova2, trt = "ShiftType")

shift_tukey2
```

Shift Type is not significantly associated with change in confidence score.

---

### FacilityYears
1. Summary Statistics
```{r facility years summary statistics conf score}
facilityyrs_sum_stats2 <- analysis_data %>%
                            dplyr::group_by(FacilityYears) %>%
                            rstatix::get_summary_stats(Delta, type = "mean_sd")
facilityyrs_sum_stats2
```

<br>

2. ANOVA
```{r facility years anova conf score}
facilityyrs_anova2 <- stats::aov(Delta ~ FacilityYears, data = analysis_data)

summary(facilityyrs_anova2)
```

<br>

3. ANOVA with Tukey Correction
```{r facility years tukey conf score}
facilityyrs_tukey2 <- agricolae::HSD.test(facilityyrs_anova2, trt = "FacilityYears")

facilityyrs_tukey2
```

Facility years is not significantly associated with change in confidence score.

---

### HealthcareYears
1. Summary Statistics
```{r healthcare years summary statistics conf score}
healthcareyrs_sum_stats2 <- analysis_data %>%
                              dplyr::group_by(HealthcareYears) %>%
                              rstatix::get_summary_stats(Delta, type = "mean_sd")
healthcareyrs_sum_stats2
```

<br>

2. ANOVA
```{r healthcare years anova conf score}
healthcareyrs_anova2 <- stats::aov(Delta ~ HealthcareYears, data = analysis_data)

summary(healthcareyrs_anova2)
```

<br>

3. ANOVA with Tukey Correction
```{r healthcare years tukey conf score}
healthcareyrs_tukey2 <- agricolae::HSD.test(healthcareyrs_anova2, trt = "HealthcareYears")

healthcareyrs_tukey2
```
Years in healthcare is not significantly associated with change in confidence score.

---

### FacilitiesNumber
1. Summary Statistics
```{r facilities number summary statistics conf score}
numfacilities_sum_stats2 <- analysis_data %>%
                              dplyr::group_by(FacilitiesNumber) %>%
                              rstatix::get_summary_stats(Delta, type = "mean_sd")
numfacilities_sum_stats2
```

<br>

2. ANOVA
```{r facilities number anova conf score}
numfacilities_anova2 <- stats::aov(Delta ~ FacilitiesNumber, data = analysis_data)

summary(numfacilities_anova2)
```

<br>

3. ANOVA with Tukey Correction
```{r facilities number tukey conf score}
numfacilities_tukey2 <- agricolae::HSD.test(numfacilities_anova2, trt = "FacilitiesNumber")

numfacilities_tukey2
```

---

## Demographics Table Summary
The last step is to create a summary table for the demographics variables with both the code identification score and the change in confidence score outcomes.
```{r demographics summary table}
#construct table for bivariate analysis of code identification score
demographics_score <- analysis_data %>%
                          gtsummary::tbl_continuous(variable = CodeScorePct,
                                                    include = c(FacilityLabel, 
                                                                PositionType,
                                                                ShiftType,
                                                                FacilityYears,
                                                                HealthcareYears,
                                                                FacilitiesNumber),
                                                    statistic = list(everything() ~ "{mean} ({sd})"),
                                                    digits = everything() ~ 1) %>%
                          add_p(test = list(everything() ~ "aov")) %>%
                          gtsummary::modify_header(stat_0 ~ "**Mean (SD)**") %>%
                          gtsummary::modify_header(statistic ~ "**F**") %>%
                          gtsummary::modify_fmt_fun(statistic ~ gtsummary::style_sigfig) %>%
                          gtsummary::bold_labels() %>%
                          gtsummary::modify_footnote(stat_0 ~ "Mean (Standard Deviation)")

demographics_score

#construct table for bivariate analysis of confidence score
demographics_conf <- analysis_data %>%
                          gtsummary::tbl_continuous(variable = Delta,
                                                    include = c(FacilityLabel, 
                                                                PositionType,
                                                                ShiftType,
                                                                FacilityYears,
                                                                HealthcareYears,
                                                                FacilitiesNumber),
                                                    statistic = list(everything() ~ "{mean} ({sd})")) %>%
                          add_p(test = list(everything() ~ "aov")) %>%
                          gtsummary::modify_header(stat_0 ~ "**Mean (SD)**") %>%
                          gtsummary::modify_header(statistic ~ "**F**") %>%
                          gtsummary::modify_fmt_fun(statistic ~ gtsummary::style_sigfig) %>%
                          gtsummary::bold_labels() %>%
                          gtsummary::modify_footnote(stat_0 ~ "Mean (Standard Deviation)")

demographics_conf

#construct table for summary numbers
demographics_count <- analysis_data %>%
                          gtsummary::select(FacilityLabel,
                                            PositionType,
                                            ShiftType,
                                            FacilityYears,
                                            HealthcareYears,
                                            FacilitiesNumber) %>%
                          gtsummary::tbl_summary() %>%
                          gtsummary::add_n() %>%
                          gtsummary::modify_header(stat_0 ~ "**n (%)**") %>%
                          gtsummary::modify_footnote(stat_0 ~ NA_character_) %>%
                          gtsummary::bold_labels()
demographics_count

#merge tables
demographics_summary <- gtsummary::tbl_merge(list(demographics_count, 
                                                  demographics_score, 
                                                  demographics_conf),
                                             tab_spanner = c(NA_character_, 
                                                             "**Code Identification Score (%)**", 
                                                             "**Change in Confidence Score**")) %>%
  
                        gtsummary::modify_column_hide(n_1) %>%
                        gtsummary::modify_caption("Table 3. Results of demographic characteristics bivariate analyses with code identification score and change in confidence score (N = 304).") %>%
                        gtsummary::modify_header(label ~ " ")
demographics_summary
```

### Save Summary Table
```{r save table}
demographics_summary_file = here::here("results", "demographics_summary_table.Rds")

saveRDS(demographics_summary, file = demographics_summary_file)
```
