---
title: "Analysis: Codes"
output: 
  html_document:
    theme: flatly
    toc: FALSE
---
<br>

---

## Introduction
This markdown imports the processed data and analyzes the data about different codes. It is broken down into the following sections:

* Data Wrangling for this analysis
* Stacked Barplot for All Questions


---

## Required Packages
The following R packages are required for this script:

* here: for path setting
* tidyverse: for all packages in the Tidyverse (ggplot2, dyplr, tidyr, readr, purr, tibble, stringr, forcats)
* extrafont: for changing ggplot fonts

```{r libraries, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)

#load required packages
library(here)
library(tidyverse)
library(extrafont)

#global environment options
# formatting for script to avoid scientific notation output
options(scipen=999)

#set ggplot theme to classic
ggplot2::theme_set(theme_classic())

#center plot titles
theme_update(plot.title = element_text(hjust = 0.5))

#load fonts
extrafont::loadfonts(device = "win")
```

---

## Load Processed Data
Load the data generated from the markdowns in the `processing_code` folder.
```{r load data}
#define file path
data_location <- here::here("data", "processed_data", "full_processed.rds")

#load data
code_data_raw <- readRDS(data_location)

```

---

## Data Wrangling
```{r data wrangling}

#only include relevant variables
code_data <- code_data_raw %>%
                  dplyr::select(c(FireType,
                                  FireAnswer,
                                  CAType,
                                  CAAnswer,
                                  PedsType,
                                  PedsAnswer,
                                  BombType,
                                  BombAnswer,
                                  ViolenceType,
                                  ViolenceAnswer,
                                  ASType,
                                  ASAnswer,
                                  InfantType,
                                  InfantAnswer,
                                  MCIType,
                                  MCIAnswer,
                                  IDType,
                                  IDAnswer,
                                  HazMatType,
                                  HazMatAnswer,
                                  MAType,
                                  MAAnswer,
                                  SWType,
                                  SWAnswer,
                                  MCType,
                                  MCAnswer,
                                  HSType,
                                  HSAnswer))

#convert to long format
code_data_long <- code_data %>%
                    tidyr::gather(question, answer, FireType:HSAnswer, factor_key = TRUE)

#create a hazard column
code_data_long$hazard <- code_data_long$question

#remove "answer" from hazard column
code_data_long$hazard <- gsub("Answer", "", code_data_long$hazard)

#remove "type" from hazard column
code_data_long$hazard <- gsub("Type", "", code_data_long$hazard)

#remove hazards from question column
code_data_long$question <- gsub("Fire", "", code_data_long$question)
code_data_long$question <- gsub("CA", "", code_data_long$question)
code_data_long$question <- gsub("Peds", "", code_data_long$question)
code_data_long$question <- gsub("Bomb", "", code_data_long$question)
code_data_long$question <- gsub("Violence", "", code_data_long$question)
code_data_long$question <- gsub("AS", "", code_data_long$question)
code_data_long$question <- gsub("Infant", "", code_data_long$question)
code_data_long$question <- gsub("MCI", "", code_data_long$question)
code_data_long$question <- gsub("ID", "", code_data_long$question)
code_data_long$question <- gsub("HazMat", "", code_data_long$question)
code_data_long$question <- gsub("MA", "", code_data_long$question)
code_data_long$question <- gsub("SW", "", code_data_long$question)
code_data_long$question <- gsub("MC", "", code_data_long$question)
code_data_long$question <- gsub("HS", "", code_data_long$question)

#rearrange columns
code_data_long <- dplyr::select(code_data_long, c(hazard,
                                                  question,
                                                  answer))

#fix value of MC "Answer"
code_data_long$question <- gsub("Mnswer", "Answer", code_data_long$question)

#convert answer to factor class
code_data_long$answer <- factor(code_data_long$answer)

#relabel hazards
code_data_long$hazard[code_data_long$hazard == "CA"] <- "Cardiac Arrest"
code_data_long$hazard[code_data_long$hazard == "Peds"] <- "Pediatric Emergency"
code_data_long$hazard[code_data_long$hazard == "Bomb"] <- "Bomb Threat"
code_data_long$hazard[code_data_long$hazard == "AS"] <- "Active Shooter"
code_data_long$hazard[code_data_long$hazard == "Infant"] <- "Infant Abduction"
code_data_long$hazard[code_data_long$hazard == "MCI"] <- "Mass Casualty"
code_data_long$hazard[code_data_long$hazard == "ID"] <- "Internal Disaster"
code_data_long$hazard[code_data_long$hazard == "HazMat"] <- "Hazardous Materials"
code_data_long$hazard[code_data_long$hazard == "MA"] <- "Missing Adult"
code_data_long$hazard[code_data_long$hazard == "SW"] <- "Severe Weather"
code_data_long$hazard[code_data_long$hazard == "MC"] <- "Missing Child"
code_data_long$hazard[code_data_long$hazard == "HS"] <- "Hostage Situation"
```

---

## Stacked Barplot for All Questions
```{r stacked barplot all}
stacked_all <- code_data_long %>%
                  dplyr::filter(question == "Answer") %>%
                  dplyr::count(hazard, answer) %>%
                  dplyr::group_by(hazard) %>%
                  dplyr::mutate(pct = prop.table(n) * 100) %>%
                  ggplot2::ggplot(aes(x = factor(hazard, levels = hazard[answer == "0"][order(pct[answer == "0"])]), 
                                      y = pct, 
                                      fill = answer,
                                      color = answer)) +
                           geom_bar(stat = "identity") +
                           geom_text(aes(label = paste0(sprintf("%1.1f", pct), "%")),
                                     position = position_stack(vjust = 0.5),
                                     size = 3,
                                     color = "white",
                                     fontface = "bold") +
                           scale_fill_manual(values = c("#BC3C29FF", "#6F99ADFF"),
                                             labels = c("Incorrect", "Correct"),
                                             name = "") +
                           scale_color_manual(values = c("#7D281B", "#4A6673")) +
                           scale_y_continuous(limits = c(0,100),
                                              expand = c(0,0)) +
                           labs(x = " ",
                                y = "Percent of Responses") +
                           theme(text = element_text(family = "Palatino Linotype"),
                                 axis.text = element_text(color = "black"),
                                 axis.text.x = element_text(angle = 90,
                                                            vjust = 0.5,
                                                            hjust = 1)) +
                           guides(color = FALSE)
stacked_all

#save file
stacked_all_fig_file = here("results", "codes", "stacked_all_codes.png")
ggsave(filename = stacked_all_fig_file, 
       plot = stacked_all,
       width = 8, height = 4.5, dpi = 300)
```

---

## Accuracy by Hazard
```{r hazard accuracy}
hazard_accuracy <- code_data_long %>%
                      dplyr::count(hazard, question, answer) %>%
                      dplyr::group_by(hazard, question) %>%
                      dplyr::mutate(pct = prop.table(n) * 100) %>%
                      ggplot2::ggplot(aes(x = question, y = pct, fill = answer))+
                               geom_bar(stat = "identity") +
                               facet_wrap(~ hazard) +

                               geom_text(aes(label = paste0(sprintf("%1.1f", pct), "%")),
                                     position = position_stack(vjust = 0.5),
                                     size = 3,
                                     color = "white",
                                     fontface = "bold") +
                               scale_fill_manual(values = c("#BC3C29FF", "#6F99ADFF"),
                                                 labels = c("Incorrect", "Correct"),
                                                 name = "") +
                               coord_flip() +
                               labs(x = "",
                                    y = "Percent of Responses") 
hazard_accuracy
```