---
title: "Analysis: MVR for Code Identification Score"
output: 
  html_document:
    theme: flatly
    toc: FALSE
---
<br>

---

## Introduction
This markdown imports the processed data and conducts a multivariate analysis for predictors with < 0.01 significance in the univariate analysis.

---

## Required Packages
The following R packages are required for this script:

* here: for path setting
* tidyverse: for all packages in the Tidyverse (ggplot2, dyplr, tidyr, readr, purr, tibble, stringr, forcats)
* broom: for making prettier outputs of regressions
* gtsummary: for making summary tables

```{r libraries, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)

#load required packages
library(here)
library(tidyverse)
library(broom)
library(gtsummary)

#global environment options
# formatting for script to avoid scientific notation output
options(scipen=999)

#set ggplot theme to classic
ggplot2::theme_set(theme_classic())

#center plot titles
ggplot2::theme_update(plot.title = element_text(hjust = 0.5))

#set gtsummary theme
gtsummary::theme_gtsummary_compact()
```

---

## Load Processed Data
Load the data generated from the markdowns in the `processing_code` folder.
```{r load data}
#define file path
data_location <- here::here("data", "processed_data", "analysis_processed.rds")

#load data
score_data <- readRDS(data_location)
```

---

## MVR Analysis: All Variables
```{r MVR all}
#subset data to include only variables with < 0.01 significance
mvr_data <- score_data %>%
              dplyr::select(FacilityLabel,
                            ShiftType,
                            FacilityYears,
                            HealthcareYears,
                            FacilitiesNumber,
                            CodeProcedures,
                            Facilitiesdifferentcodes,
                            CodePreference,
                            Codeexceptions,
                            TrainingOrientation,
                            TrainingExercises,
                            TrainingYearly,
                            CodeScorePct)

#MVR with all variables
mvr_fit <- stats::glm(CodeScorePct ~ . , data = mvr_data)

#MVR summary
summary(mvr_fit)

broom::tidy(mvr_fit)

broom::glance(mvr_fit)
```
In this model, Facilities B/C/D, 4-5 facilities worked, Knowledge of Activation Procedure for Codes, and training at orientation are significant. Facility E, 2-5 years at facility, >5 facilities, and exceptions to plain language are marginally significant.

R squared = 0.439
logLik = -1242.14
AIC = 2536.28
BIC = 2632.923

---

## Create Regression Summary Table
```{r regression table}
uvregression_table <- score_data %>%
                        gtsummary::select(FacilityLabel,
                                          PositionType,
                                          ShiftType,
                                          FacilityYears,
                                          HealthcareYears,
                                          FacilitiesNumber,
                                          CodeProcedures,
                                          Codeconfusion,
                                          Facilitiesdifferentcodes,
                                          CodePreference,
                                          Codeexceptions,
                                          TrainingOrientation,
                                          TrainingExercises,
                                          TrainingYearly,
                                          Traininglasttime,
                                          CodeScorePct) %>%
                        gtsummary::tbl_uvregression(method = glm,
                                                    y = CodeScorePct,
                                                    estimate_fun = ~ gtsummary::style_sigfig(.x, digits = 3),
                                                    pvalue_fun = ~ gtsummary::style_pvalue(.x, digits = 2)) %>%
                        gtsummary::bold_p(t = 0.05) %>%
                        gtsummary::bold_labels()

uvregression_table

#significant variables: Facility, ShiftType, FacilityYears, HealthcareYears, FacilitiesNumber, CodeProcedures, Facilitiesdifferentcodes, CodePreference, Codeexceptions, TrainingOrientation, TrainingExercises, TrainingYearly
#build mvr table
mvr_table <- mvr_fit %>%            
                gtsummary::tbl_regression(estimate_fun = ~ gtsummary::style_sigfig(.x, digits = 3),
                                          pvalue_fun = ~ gtsummary::style_pvalue(.x, digits = 2)) %>%
                gtsummary::bold_labels() %>%
                gtsummary::bold_p(t = 0.05)
mvr_table

#merge tables
regression_table <- gtsummary::tbl_merge(list(uvregression_table,
                                              mvr_table),
                                              tab_spanner = c("**Univariate**", 
                                                             "**Multivariate**")) %>%
                    gtsummary::modify_caption("Table 5. Results of regression analyses for code identification score. Only variables significantly associated with code identification score (< 0.05) were included in the multivariate regression.") %>%
                    gtsummary::modify_header(label ~ " ")
regression_table

#save table
regression_tbl_file = here::here("results", "regression_table.Rds")

saveRDS(regression_table, file = regression_tbl_file)
```

