---
title: "Analysis: Bivariate Analysis for Experience with Code Variables"
output: 
  html_document:
    theme: flatly
    toc: FALSE
---
<br>

---

## Introduction
This markdown imports the processed analysis data and conducts a bivariate analysis for the outcomes of interest: change in confidence score and code identification score.

The following variables representing experience with codes are included:

* CodeProcedures
* Codeconfusion
* Facilitiesdifferentcodes
* CodePreference
* Codeexceptions
* TrainingOrientation
* TrainingExercises
* TrainingYearly
* Traininglasttime

For each variable, the following steps are taken:

* Summary statistics
* ANOVA
* ANOVA with Tukey correction
* Box Plot Visualization if significant

---

## Required Packages
The following R packages are required for this script:

* here: for path setting
* tidyverse: for all packages in the Tidyverse (ggplot2, dyplr, tidyr, readr, purr, tibble, stringr, forcats)
* rstatix: for summary stats
* agricolae: for more detailed output of Tukey HSD
* broom: for making prettier outputs of regressions
* ggpubr: for making box plots of significant variables
* gtsummary: for making summary tables

```{r libraries, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)

#load required packages
library(here)
library(tidyverse)
library(rstatix)
library(agricolae)
library(broom)
library(ggpubr)
library(gtsummary)

#global environment options
# formatting for script to avoid scientific notation output
options(scipen=999)

#set ggplot theme to classic
ggplot2::theme_set(theme_classic())

#center plot titles
ggplot2::theme_update(plot.title = element_text(hjust = 0.5))

#set gtsummary theme
gtsummary::theme_gtsummary_compact()
```

---

## Load Processed Data
Load the data generated from the markdowns in the `processing_code` folder.
```{r load data}
#define file path
data_location <- here::here("data", "processed_data", "analysis_processed.rds")

#load data
analysis_data <- readRDS(data_location)
```

---

## Code Identification Score
Each variable will be analyzed where y = `CodeScorePct` (the percent of correctly identified codes during the survey).

---

### Code Procedures

1. Summary Statistics
```{r code procedures summary statistics code ID}
procedures_sum_stats1 <- analysis_data %>%
                          dplyr::group_by(CodeProcedures) %>%
                          rstatix::get_summary_stats(CodeScorePct, type = "mean_sd")
procedures_sum_stats1
```

<br>

2. ANOVA
```{r code procedures anova code ID}
procedures_anova1 <- stats::aov(CodeScorePct ~ CodeProcedures, data = analysis_data)

summary(procedures_anova1)
```

<br>

3. ANOVA with Tukey Correction
```{r code procedures tukey code ID}
procedures_tukey1 <- agricolae::HSD.test(procedures_anova1, trt = "CodeProcedures")

procedures_tukey1
```

There is a significant difference between the means. 

---

### Code confusion

1. Summary Statistics
```{r code confusion summary statistics code ID}
confusion_sum_stats1 <- analysis_data %>%
                          dplyr::group_by(Codeconfusion) %>%
                          rstatix::get_summary_stats(CodeScorePct, type = "mean_sd")
confusion_sum_stats1
```

<br>

2. ANOVA
```{r code confusion anova code ID}
confusion_anova1 <- stats::aov(CodeScorePct ~ Codeconfusion, data = analysis_data)

summary(confusion_anova1)
```

<br>

3. ANOVA with Tukey Correction
```{r code confusion tukey code ID}
confusion_tukey1 <- agricolae::HSD.test(confusion_anova1, trt = "Codeconfusion")

confusion_tukey1
```
There is not a significant difference in the mean code identification score by code confusion.

---

### Facilities with different codes

1. Summary Statistics
```{r facilities diff summary statistics code ID}
facdiff_sum_stats1 <- analysis_data %>%
                        dplyr::group_by(Facilitiesdifferentcodes) %>%
                        rstatix::get_summary_stats(CodeScorePct, type = "mean_sd")
facdiff_sum_stats1
```

<br>

2. ANOVA
```{r facilities diff anova code ID}
facdiff_anova1 <- stats::aov(CodeScorePct ~ Facilitiesdifferentcodes, data = analysis_data)

summary(facdiff_anova1)
```

<br>

3. ANOVA with Tukey Correction
```{r facilities diff tukey code ID}
facdiff_tukey1 <- agricolae::HSD.test(facdiff_anova1, trt = "Facilitiesdifferentcodes")

facdiff_tukey1
```
There is not a significant difference in the mean code identification score by facilities with different codes.

---

### Code Preference

1. Summary Statistics
```{r code preference summary statistics code ID}
preference_sum_stats1 <- analysis_data %>%
                            dplyr::group_by(CodePreference) %>%
                            rstatix::get_summary_stats(CodeScorePct, type = "mean_sd")
preference_sum_stats1
```

<br>

2. ANOVA
```{r code preference anova code ID}
preference_anova1 <- stats::aov(CodeScorePct ~ CodePreference, data = analysis_data)

summary(preference_anova1)
```

<br>

3. ANOVA with Tukey Correction
```{r code preference tukey code ID}
preference_tukey1 <- agricolae::HSD.test(preference_anova1, trt = "CodePreference")

preference_tukey1
```

There is a significant difference in the mean score between those who prefer color codes and those who prefer plain language codes.

---

### Codeexceptions

1. Summary Statistics
```{r code exceptions summary statistics code ID}
exceptions_sum_stats1 <- analysis_data %>%
                              dplyr::group_by(Codeexceptions) %>%
                              rstatix::get_summary_stats(CodeScorePct, type = "mean_sd")
exceptions_sum_stats1
```

<br>

2. ANOVA
```{r code exceptions anova code ID}
exceptions_anova1 <- stats::aov(CodeScorePct ~ Codeexceptions, data = analysis_data)

summary(exceptions_anova1)
```

<br>

3. ANOVA with Tukey Correction
```{r code exceptions tukey code ID}
exceptions_tukey1 <- agricolae::HSD.test(exceptions_anova1, trt = "Codeexceptions")

exceptions_tukey1
```
There is a significant difference in the mean score for those who believe some codes should remain color and those who believe all codes should be plain language.

---

### TrainingOrientation

1. Summary Statistics
```{r orientation summary statistics code ID}
orientation_sum_stats1 <- analysis_data %>%
                              dplyr::group_by(TrainingOrientation) %>%
                              rstatix::get_summary_stats(CodeScorePct, type = "mean_sd")
orientation_sum_stats1
```

<br>

2. ANOVA
```{r orientation anova code ID}
orientation_anova1 <- stats::aov(CodeScorePct ~ TrainingOrientation, data = analysis_data)

summary(orientation_anova1)
```

<br>

3. ANOVA with Tukey Correction
```{r orientation tukey code ID}
orientation_tukey1 <- agricolae::HSD.test(orientation_anova1, trt = "TrainingOrientation")

orientation_tukey1
```
There is a significant difference in the mean of score by training at orientation.

---

### Training During Drills/Exercises

1. Summary Statistics
```{r exercises summary statistics code ID}
exercises_sum_stats1 <- analysis_data %>%
                              dplyr::group_by(TrainingExercises) %>%
                              rstatix::get_summary_stats(CodeScorePct, type = "mean_sd")
exercises_sum_stats1
```

<br>

2. ANOVA
```{r exercises anova code ID}
exercises_anova1 <- stats::aov(CodeScorePct ~ TrainingExercises, data = analysis_data)

summary(exercises_anova1)
```

<br>

3. ANOVA with Tukey Correction
```{r exercises tukey code ID}
exercises_tukey1 <- agricolae::HSD.test(exercises_anova1, trt = "TrainingExercises")

exercises_tukey1
```
There is a significant difference in the mean of score by training during drills/exercises.

---

### Training Yearly

1. Summary Statistics
```{r yearly summary statistics code ID}
yearly_sum_stats1 <- analysis_data %>%
                          dplyr::group_by(TrainingYearly) %>%
                          rstatix::get_summary_stats(CodeScorePct, type = "mean_sd")
yearly_sum_stats1
```

<br>

2. ANOVA
```{r yearly anova code ID}
yearly_anova1 <- stats::aov(CodeScorePct ~ TrainingYearly, data = analysis_data)

summary(yearly_anova1)
```

<br>

3. ANOVA with Tukey Correction
```{r yearly tukey code ID}
yearly_tukey1 <- agricolae::HSD.test(yearly_anova1, trt = "TrainingYearly")

yearly_tukey1
```
There is a significant difference in the mean of score by annual training.

---

### Training Last Time

1. Summary Statistics
```{r training last summary statistics code ID}
lasttrain_sum_stats1 <- analysis_data %>%
                          dplyr::group_by(Traininglasttime) %>%
                          rstatix::get_summary_stats(CodeScorePct, type = "mean_sd")
lasttrain_sum_stats1
```

<br>

2. ANOVA
```{r lasttrain anova code ID}
lasttrain_anova1 <- stats::aov(CodeScorePct ~ Traininglasttime, data = analysis_data)

summary(lasttrain_anova1)
```

<br>

3. ANOVA with Tukey Correction
```{r lasttrain tukey code ID}
lasttrain_tukey1 <- agricolae::HSD.test(lasttrain_anova1, trt = "Traininglasttime")

lasttrain_tukey1
```
There is not a significant difference in mean score by date of last training.

---

## Change in Confidence Score
Each variable will be analyzed where y = `Delta` (the change in confidence score pre/post survey).

---

### Code Procedures

1. Summary Statistics
```{r code procedures summary statistics conf score}
procedures_sum_stats2 <- analysis_data %>%
                          dplyr::group_by(CodeProcedures) %>%
                          rstatix::get_summary_stats(Delta, type = "mean_sd")
procedures_sum_stats2
```

<br>

2. ANOVA
```{r code procedures anova conf score}
procedures_anova2 <- stats::aov(Delta ~ CodeProcedures, data = analysis_data)

summary(procedures_anova2)
```

<br>

3. ANOVA with Tukey Correction
```{r code procedures tukey conf score}
procedures_tukey2 <- agricolae::HSD.test(procedures_anova2, trt = "CodeProcedures")

procedures_tukey2
```

There is not a significant difference between the means. 

---

### Code confusion

1. Summary Statistics
```{r code confusion summary statistics conf score}
confusion_sum_stats2 <- analysis_data %>%
                          dplyr::group_by(Codeconfusion) %>%
                          rstatix::get_summary_stats(Delta, type = "mean_sd")
confusion_sum_stats2
```

<br>

2. ANOVA
```{r code confusion anova conf score}
confusion_anova2 <- stats::aov(Delta ~ Codeconfusion, data = analysis_data)

summary(confusion_anova2)
```

<br>

3. ANOVA with Tukey Correction
```{r code confusion tukey conf score}
confusion_tukey2 <- agricolae::HSD.test(confusion_anova2, trt = "Codeconfusion")

confusion_tukey2
```
There is not a significant difference in the mean change in confidence score by code confusion.

---

### Facilities with different codes

1. Summary Statistics
```{r facilities diff summary statistics conf score}
facdiff_sum_stats2 <- analysis_data %>%
                        dplyr::group_by(Facilitiesdifferentcodes) %>%
                        rstatix::get_summary_stats(Delta, type = "mean_sd")
facdiff_sum_stats2
```

<br>

2. ANOVA
```{r facilities diff anova conf score}
facdiff_anova2 <- stats::aov(Delta ~ Facilitiesdifferentcodes, data = analysis_data)

summary(facdiff_anova2)
```

<br>

3. ANOVA with Tukey Correction
```{r facilities diff tukey conf score}
facdiff_tukey2 <- agricolae::HSD.test(facdiff_anova2, trt = "Facilitiesdifferentcodes")

facdiff_tukey2
```
There is not a significant difference in the mean change in confidence score by facilities with different codes.

---

### Code Preference

1. Summary Statistics
```{r code preference summary statistics conf score}
preference_sum_stats2 <- analysis_data %>%
                            dplyr::group_by(CodePreference) %>%
                            rstatix::get_summary_stats(Delta, type = "mean_sd")
preference_sum_stats2
```

<br>

2. ANOVA
```{r code preference anova conf score}
preference_anova2 <- stats::aov(Delta ~ CodePreference, data = analysis_data)

summary(preference_anova2)
```

<br>

3. ANOVA with Tukey Correction
```{r code preference tukey conf score}
preference_tukey2 <- agricolae::HSD.test(preference_anova2, trt = "CodePreference")

preference_tukey2
```

There is a not a significant difference between the means of change in confidence score.

---

### Codeexceptions

1. Summary Statistics
```{r code exceptions summary statistics conf score}
exceptions_sum_stats2 <- analysis_data %>%
                              dplyr::group_by(Codeexceptions) %>%
                              rstatix::get_summary_stats(Delta, type = "mean_sd")
exceptions_sum_stats2
```

<br>

2. ANOVA
```{r code exceptions anova conf score}
exceptions_anova2 <- stats::aov(Delta ~ Codeexceptions, data = analysis_data)

summary(exceptions_anova2)
```

<br>

3. ANOVA with Tukey Correction
```{r code exceptions tukey conf score}
exceptions_tukey2 <- agricolae::HSD.test(exceptions_anova2, trt = "Codeexceptions")

exceptions_tukey2
```
There is a not a significant difference between the means of change in confidence score.

---

### TrainingOrientation

1. Summary Statistics
```{r orientation summary statistics conf score}
orientation_sum_stats2 <- analysis_data %>%
                              dplyr::group_by(TrainingOrientation) %>%
                              rstatix::get_summary_stats(Delta, type = "mean_sd")
orientation_sum_stats2
```

<br>

2. ANOVA
```{r orientation anova conf score}
orientation_anova2 <- stats::aov(Delta ~ TrainingOrientation, data = analysis_data)

summary(orientation_anova2)
```

<br>

3. ANOVA with Tukey Correction
```{r orientation tukey conf score}
orientation_tukey2 <- agricolae::HSD.test(orientation_anova2, trt = "TrainingOrientation")

orientation_tukey2
```
There is a not a significant difference between the means of change in confidence score.

---

### Training During Drills/Exercises

1. Summary Statistics
```{r exercises summary statistics conf score}
exercises_sum_stats2 <- analysis_data %>%
                              dplyr::group_by(TrainingExercises) %>%
                              rstatix::get_summary_stats(Delta, type = "mean_sd")
exercises_sum_stats2
```

<br>

2. ANOVA
```{r exercises anova conf score}
exercises_anova2 <- stats::aov(Delta ~ TrainingExercises, data = analysis_data)

summary(exercises_anova2)
```

<br>

3. ANOVA with Tukey Correction
```{r exercises tukey conf score}
exercises_tukey2 <- agricolae::HSD.test(exercises_anova2, trt = "TrainingExercises")

exercises_tukey2
```
There is a not a significant difference between the means of change in confidence score.

---

### Training Yearly

1. Summary Statistics
```{r yearly summary statistics conf score}
yearly_sum_stats2 <- analysis_data %>%
                          dplyr::group_by(TrainingYearly) %>%
                          rstatix::get_summary_stats(Delta, type = "mean_sd")
yearly_sum_stats2
```

<br>

2. ANOVA
```{r yearly anova conf score}
yearly_anova2 <- stats::aov(Delta ~ TrainingYearly, data = analysis_data)

summary(yearly_anova2)
```

<br>

3. ANOVA with Tukey Correction
```{r yearly tukey conf score}
yearly_tukey2 <- agricolae::HSD.test(yearly_anova2, trt = "TrainingYearly")

yearly_tukey2
```
There is a significant difference in the mean change in confidence score by annual training.

---

### Training Last Time

1. Summary Statistics
```{r training last summary statistics conf score}
lasttrain_sum_stats2 <- analysis_data %>%
                          dplyr::group_by(Traininglasttime) %>%
                          rstatix::get_summary_stats(Delta, type = "mean_sd")
lasttrain_sum_stats2
```

<br>

2. ANOVA
```{r lasttrain anova conf score}
lasttrain_anova2 <- stats::aov(Delta ~ Traininglasttime, data = analysis_data)

summary(lasttrain_anova2)
```

<br>

3. ANOVA with Tukey Correction
```{r lasttrain tukey conf score}
lasttrain_tukey2 <- agricolae::HSD.test(lasttrain_anova2, trt = "Traininglasttime")

lasttrain_tukey2
```
There is a not a significant difference between the means of change in confidence score.

---

## Experience with Codes Table Summary
The last step is to create a summary table for the experience variables with both the code identification score and the change in confidence score outcomes.
```{r experience summary table}
#construct table for bivariate analysis of code identification score
experience_score <- analysis_data %>%
                          gtsummary::tbl_continuous(variable = CodeScorePct,
                                                    include = c(CodeProcedures,
                                                                Codeconfusion,
                                                                Facilitiesdifferentcodes,
                                                                CodePreference,
                                                                Codeexceptions,
                                                                TrainingOrientation,
                                                                TrainingExercises,
                                                                TrainingYearly,
                                                                Traininglasttime),
                                                    statistic = list(everything() ~ "{mean} ({sd})"),
                                                    digits = everything() ~ 1) %>%
                          add_p(test = list(everything() ~ "aov")) %>%
                          gtsummary::modify_header(stat_0 ~ "**Mean (SD)**") %>%
                          gtsummary::modify_header(statistic ~ "**F**") %>%
                          gtsummary::modify_fmt_fun(statistic ~ gtsummary::style_sigfig) %>%
                          gtsummary::bold_labels() %>%
                          gtsummary::modify_footnote(stat_0 ~ "Mean (Standard Deviation)")

experience_score

#construct table for bivariate analysis of confidence score
experience_conf <- analysis_data %>%
                          gtsummary::tbl_continuous(variable = Delta,
                                                    include = c(CodeProcedures,
                                                                Codeconfusion,
                                                                Facilitiesdifferentcodes,
                                                                CodePreference,
                                                                Codeexceptions,
                                                                TrainingOrientation,
                                                                TrainingExercises,
                                                                TrainingYearly,
                                                                Traininglasttime),
                                                    statistic = list(everything() ~ "{mean} ({sd})")) %>%
                          add_p(test = list(everything() ~ "aov")) %>%
                          gtsummary::modify_header(stat_0 ~ "**Mean (SD)**") %>%
                          gtsummary::modify_header(statistic ~ "**F**") %>%
                          gtsummary::modify_fmt_fun(statistic ~ gtsummary::style_sigfig) %>%
                          gtsummary::bold_labels() %>%
                          gtsummary::modify_footnote(stat_0 ~ "Mean (Standard Deviation)")

experience_conf

#construct table for summary numbers
experience_count <- analysis_data %>%
                          gtsummary::select(CodeProcedures,
                                            Codeconfusion,
                                            Facilitiesdifferentcodes,
                                            CodePreference,
                                            Codeexceptions,
                                            TrainingOrientation,
                                            TrainingExercises,
                                            TrainingYearly,
                                            Traininglasttime) %>%
                          gtsummary::tbl_summary() %>%
                          gtsummary::add_n() %>%
                          gtsummary::modify_header(stat_0 ~ "**n (%)**") %>%
                          gtsummary::modify_footnote(stat_0 ~ NA_character_) %>%
                          gtsummary::bold_labels()
experience_count

#merge tables
experience_summary <- gtsummary::tbl_merge(list(experience_count, experience_score, experience_conf),
                                           tab_spanner = c(NA_character_, "**Code Identification Score (%)**", "**Change in Confidence Score**")) %>%
                      gtsummary::modify_column_hide(n_1) %>%
                      gtsummary::modify_caption("Table 4. Results of experience with emergency codes bivariate analyses with code identification score and change in confidence score (N = 304).") %>%
                      gtsummary::modify_header(label ~ " ")

experience_summary
  
```

### Save Summary Table
```{r save table}
experience_summary_file = here::here("results", "experience_summary_table.Rds")

saveRDS(experience_summary, file = experience_summary_file)
```
