---
title: "Data Processing: Combining All"
output: 
  html_document:
    theme: flatly
    toc: FALSE
---

<br>

---

## Introduction
This markdown loads the graded dataframes for each facility and combines them into one overall dataset.

---

## Required Packages
The following R packages are required for this script:

* here: for path setting
* readxl: for importing Excel data
* skimr: for data summarization
* tidyverse: for using all packages in the Tidyverse for data wrangling (ggplot2, dplyr, tidyr, readr, purr, tibble, stringr, and forcats)
* stringr: for filtering training variable

```{r libraries, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#load required packages
library(here)
library(readxl)
library(skimr)
library(tidyverse)
library(stringr)
```

---

## Load Graded Facility Data
Load the graded data saved in the `graded_data` folder.
```{r load data}
#define path to data
data_location1 <- here::here("data","graded_data","FacilityA_grades_processed.xlsx")
data_location2 <- here::here("data", "graded_data", "FacilityB_grades_processed.xlsx")
data_location3 <- here::here("data", "graded_data", "FacilityC_grades_processed.xlsx")
data_location4 <- here::here("data", "graded_data", "FacilityD_grades_processed.xlsx")
data_location5 <- here::here("data", "graded_data", "FacilityE_grades_processed.xlsx")

#load data
FacilityA <- readxl::read_xlsx(data_location1, sheet = "Sheet1")
FacilityB <- readxl::read_xlsx(data_location2, sheet = "Sheet1")
FacilityC <- readxl::read_xlsx(data_location3, sheet = "Sheet1")
FacilityD <- readxl::read_xlsx(data_location4, sheet = "Sheet1")
FacilityE <- readxl::read_xlsx(data_location5, sheet = "Sheet1")

```

---

## Column Names
Before we can combine the DFs, we need to make sure all of the DFs have the same column names. We are using `FacilityB` as the reference one as an arbitrary choice.
```{r same column names}
names(FacilityA) <- names(FacilityB)
names(FacilityC) <- names(FacilityB)
names(FacilityD) <- names(FacilityB)
names(FacilityE) <- names(FacilityB)
```

---

## Combine Graded DF
Now we can combine the six graded data frames into one overall dataset.
```{r combine facility dfs}
overall_1 <- rbind(FacilityA, FacilityB, FacilityC, FacilityD, FacilityE)
```

---

## Cleaning Variables
We need to streamline the more open-ended answers so that they have a common format.
```{r data cleaning}
#EC-YN variable
overall_1$`EC-YN`[overall_1$`EC-YN` == "NO"] <- "No"
overall_1$`EC-YN`[overall_1$`EC-YN` == "YES (If so, please explain.)"] <- "Yes"

#PL-codes variable
overall_1$`PL-codes`[overall_1$`PL-codes` == "NO, color codes are better."] <- "Color Codes"
overall_1$`PL-codes`[overall_1$`PL-codes` == "NO, color codes are better. (If so, why?)"] <- "Color Codes"
overall_1$`PL-codes`[overall_1$`PL-codes` == "YES, I would prefer plain language codes.  (If so, why?)
"] <- "Plain Language"
overall_1$`PL-codes`[overall_1$`PL-codes` == "YES, I would prefer plain language codes.  (If so, why?)"] <- "Plain Language"
overall_1$`PL-codes`[overall_1$`PL-codes` == "NOT APPLICABLE, my facility already utilizes plain language codes."] <- "Plain Language"
overall_1$`PL-codes`[overall_1$`PL-codes` == "NOT APPLICABLE,  my facility already utilizes plain language codes."] <- "Plain Language"

#Code-exceptions variable
overall_1$`Code-exceptions`[overall_1$`Code-exceptions` == "NO (Plain language should be used for all codes.)"] <- "No"
overall_1$`Code-exceptions`[overall_1$`Code-exceptions` == "YES (If so, which specific codes should remain colors?)"] <- "Yes"

#Training-last-time variable
overall_1$`Training-last-time`[overall_1$`Training-last-time` == "Within the last month"] <- "< 1 month"
overall_1$`Training-last-time`[overall_1$`Training-last-time` == "1-6 months ago"] <- "1-6 months"
overall_1$`Training-last-time`[overall_1$`Training-last-time` == "6 months - 1 year ago"] <- "6-12 months"
overall_1$`Training-last-time`[overall_1$`Training-last-time` == "More than 1 year ago"] <- "> 1 year"

#Training -- we have to first create separate variables for each training category
overall_1$`Training-Orientation` <- stringr::str_count(overall_1$Training, "Training during employee orientation")
overall_1$`Training-Yearly` <- stringr::str_count(overall_1$Training, "Yearly refresher training")
overall_1$`Training-Exercises` <- stringr::str_count(overall_1$Training, "Drills and exercises")
overall_1$`Training-OtherCat` <- stringr::str_count(overall_1$Training, "Other (indicate below)")

#now convert all of them to yes/no variables
overall_1$`Training-Orientation`[overall_1$`Training-Orientation` == 1] <- "Yes"
overall_1$`Training-Orientation`[overall_1$`Training-Orientation` == 0] <- "No"

overall_1$`Training-Yearly`[overall_1$`Training-Yearly` == 1] <- "Yes"
overall_1$`Training-Yearly`[overall_1$`Training-Yearly` == 0] <- "No"

overall_1$`Training-Exercises`[overall_1$`Training-Exercises` == 1] <- "Yes"
overall_1$`Training-Exercises`[overall_1$`Training-Exercises` == 0] <- "No"

overall_1$`Training-OtherCat`[overall_1$`Training-OtherCat` == 1] <- "Yes"
overall_1$`Training-OtherCat`[overall_1$`Training-OtherCat` == 0] <- "No"
```

We need to reorder the columns after introducing the new training variables.
```{r reorder columns}
overall_2 <- overall_1 %>%
                dplyr::select(`Facility-Label`:`Code-exceptions-ID`,
                              `Training-Orientation`,
                              `Training-Yearly`,
                              `Training-Exercises`,
                              `Training-OtherCat`,
                              `Training-other`,
                              `Training-last-time`,
                              `Facilities-different-codes`,
                              `Code-confusion`,
                              `Post-Confidence`)
```

Before saving the processed dataset, let's look at the summary to see if there's anything else we need to clean.
```{r processed overview check}
#use the skimr package as the base R summary function won't tell us much
skimr::skim(overall_2)
```

---

## Final Adjustments
The variables are all of the right class. The only adjustment is to drop the one observation that does not have a 100% completion of the survey.
Row 54 corresponds to one of the members of the research team testing the survey and does not actually represent a participant. Therefore, it needs to be removed.

We need to also remove the observation with 152 years worked at the facility.
```{r remove false data}
#only keep if percent completion is 100%
overall_3 <- overall_2[overall_2$`percent-completed` == 100, ]

overall_4 <- overall_3[overall_3$`Facility-Years` < 152, ]
```

---

## Save Overall DF
We can now save the combined dataset.
```{r save cleaned dataset}
#make a copy of last iteration in case other steps have to be added later
overall_processed <- overall_4

#location to save dataframe
overall_processed_location <- here::here("data", "processed_data", "combined_processed.rds")
overall_processed_location2 <- here::here("data", "processed_data", "combined_processed.xlsx")

#save data as RDS
saveRDS(overall_processed, file = overall_processed_location)

#export as Excel file
writexl::write_xlsx(overall_processed, overall_processed_location2)
```