---
title: "Analysis: Answer Key Table"
output: 
  html_document:
    theme: flatly
    toc: FALSE
---
<br>

---

## Introduction
This markdown imports combined processed dataframe and prepares it for analysis of the confidence scores and code identification scores.

The workflow includes the following steps:

1. Drop variables relating to specific codes
2. Categorize all variables as 0, 1, 2, ...
3. Convert Code Identification score to percentage
4. Define `delta` to be change in confidence score
5. Drop any remaining unnecessary variables
6. Save newly processed dataframe for analysis

---

## Required Packages
The following R packages are required for this script:

* here: for path setting
* tidyverse: for all packages in the Tidyverse (ggplot2, dyplr, tidyr, readr, purr, tibble, stringr, forcats)
* table1: for labeling variable names
* writexl: for exporting excel files

```{r libraries, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)

#load required packages
library(here) #to set paths
library(tidyverse) #for data processing
library(table1) #for labeling variable names
library(writexl) #for exporting excel files
```

---

## Load Data
Load the answer key .csv from the `raw_data` folder.
```{r load data}
#define file path
data_location <- here::here("data", "processed_data", "combined_processed.rds")

#load data
processed <- readRDS(data_location)
```

---

## 1. Drop Varaibles relating to specific codes
```{r drop codes}
#drop specific code columns
analysis_1 <- processed %>%
                  dplyr::select(-c("percent-completed"))

#remove dashes from column names
names(analysis_1) <- gsub("-", "", names(analysis_1))
```

---

## 2. Discretize / categorize variables
Going one by one through the variables, we will define factors and labels.

**FacilityLabel**
```{r facility label}
#categories and counts
table(analysis_1$FacilityLabel)

#assign levels of factor
analysis_1$FacilityLabel <- factor(analysis_1$FacilityLabel,
                                   levels = c("A", "B", "C", "D", "E"))

#label variable
table1::label(analysis_1$FacilityLabel) <- "Facility"
  
```
<br>

**ClinicalNon**
```{r clinicalnon}
#categories and counts
table(analysis_1$ClinicalNon)

#assign levels of factor
analysis_1$ClinicalNon <- factor(analysis_1$ClinicalNon,
                                   levels = c("Clinical", "Non-clinical"))

#label variable
table1::label(analysis_1$ClinicalNon) <- "Position Type"
```

<br>

**HealthcareYears**
```{r healthcare years}
#categories and counts
table(analysis_1$HealthcareYears)

#assign levels of factor
analysis_1$HealthcareYears <- factor(analysis_1$HealthcareYears,
                                     levels = c("0-2 years", "2-5 years", "5-8 years", "> 8 years"))

#label variable
table1::label(analysis_1$HealthcareYears) <- "Healthcare Experience"
```

<br>

**FacilityYears**
```{r facility years}
#this is a continuous variable, so we need to first figure out appropriate categories
summary(analysis_1$FacilityYears)

#we can just use the same categories as healthcare experience: 0-2, 2-5, 5-8, > 8
#assign categories
analysis_1$FacilityYears <- cut(analysis_1$FacilityYears,
                                breaks = c(-Inf, 2, 5, 8, Inf),
                                labels = c("0-2 years", "2-5 years", "5-8 years", "> 8 years"))

#categories and counts
table(analysis_1$FacilityYears)

#assign levels of factor -- already taken care of in previous step

#label variable
table1::label(analysis_1$FacilityYears) <- "Facility Experience"
```

<br>

**FacilitiesNumber**
```{r facilities number}
#this is a continuous variable, so we need to first figure out appropriate categories
summary(analysis_1$FacilitiesNumber)

#0 facilities corresponds to researchers validating data, so remove them
analysis_2 <- subset(analysis_1,
                     analysis_1$FacilitiesNumber != 0)

#use: "1 facility, 2-3 facilities, 3-5 facilities, > 5 facilities
analysis_2$FacilitiesNumber <- cut(analysis_2$FacilitiesNumber,
                                   breaks = c(-Inf, 1.9, 3.9, 5, Inf),
                                   labels = c("1 facility", "2-3 facilities", "4-5 facilities", "> 5 facilities"))

#categories and counts
table(analysis_2$FacilitiesNumber)

#assign levels of factor -- already taken care of in previous step

#label variable
table1::label(analysis_2$FacilitiesNumber) <- "Total Facilities in Career"
```

<br>

**ShiftType**
```{r shift type}
#categories and counts
table(analysis_2$ShiftType)

#assign levels of factor
analysis_2$ShiftType <- factor(analysis_2$ShiftType,
                               levels = c("Day Shift", "Night Shift", "Equal times on both shifts"))

#label variable
table1::label(analysis_2$ShiftType) <- "Typical Shift"
```

<br>

**ECYN**
```{r ecyn}
#categories and counts
table(analysis_2$ECYN)

#assign levels of factor
analysis_2$ECYN <- factor(analysis_2$ECYN,
                          levels = c("No", "Yes"))

#label variable
table1::label(analysis_2$ECYN) <- "Knowledge of Code Activation Procedures"
```

<br>

**PLcodes**
```{r PL codes}
#categories and counts
table(analysis_2$PLcodes)

#assign levels of factor
analysis_2$PLcodes <- factor(analysis_2$PLcodes,
                             levels = c("Color Codes", "Plain Language"))

#label variable
table1::label(analysis_2$PLcodes) <- "Code Type Preference"
```

<br>

**Codeexceptions**
```{r code exceptions}
#categories and counts
table(analysis_2$Codeexceptions)

#assign levels of factor
analysis_2$Codeexceptions <- factor(analysis_2$Codeexceptions,
                                    levels = c("No", "Yes"))

#label variable
table1::label(analysis_2$Codeexceptions) <- "Exceptions for Plain Language Codes"
```

<br>

**TrainingOrientation**
```{r training orientation}
#categories and counts
table(analysis_2$TrainingOrientation)

#assign levels of factor
analysis_2$TrainingOrientation <- factor(analysis_2$TrainingOrientation,
                                  levels = c("No", "Yes"))

#label variable
table1::label(analysis_2$TrainingOrientation) <- "Training at Orientation"
```

<br>

**TrainingYearly**
```{r training yearly}
#categories and counts
table(analysis_2$TrainingYearly)

#assign levels of factor
analysis_2$TrainingYearly <- factor(analysis_2$TrainingYearly,
                                    levels = c("No", "Yes"))

#label variable
table1::label(analysis_2$TrainingYearly) <- "Annual Training"
```

<br>

**TrainingExercises**
```{r training exercises}
#categories and counts
table(analysis_2$TrainingExercises)

#assign levels of factor
analysis_2$TrainingExercises <- factor(analysis_2$TrainingExercises,
                                       levels = c("No", "Yes"))

#label variable
table1::label(analysis_2$TrainingExercises) <- "Training During Drills/Exercises"
```

<br>

**Traininglasttime**
```{r training last time}
#categories and counts
table(analysis_2$Traininglasttime)

#assign levels of factor
analysis_2$Traininglasttime <- factor(analysis_2$Traininglasttime,
                                      levels = c("< 1 month", "1-6 months", "6-12 months", "> 1 year"))

#label variable
table1::label(analysis_2$Traininglasttime) <- "Time Since Last Training"
```

<br>

**Facilitiesdifferentcodes**
```{r facilities different codes}
#categories and counts
table(analysis_2$Facilitiesdifferentcodes)

#assign levels of factor
analysis_2$Facilitiesdifferentcodes <- factor(analysis_2$Facilitiesdifferentcodes,
                                              levels = c("No", "Yes", "Maybe"))

#label variable
table1::label(analysis_2$Facilitiesdifferentcodes) <- "Worked at a Facility with Different Color Codes"
```

<br>

**Codeconfusion**
```{r code confusion}
#categories and counts
table(analysis_2$Codeconfusion)

#assign levels of factor
analysis_2$Codeconfusion <- factor(analysis_2$Codeconfusion,
                                   levels = c("No", "Yes"))

#label variable
table1::label(analysis_2$Codeconfusion) <- "Witnessed Code Confusion"
```

---

## 3. Convert `GradeAnswer` to percentage
```{r grade answer}
#multiply by 100 (but creating dummy variable just in case)
analysis_2$GradeAnswerPct <- analysis_2$GradeAnswer * 100

#label variables
table1::label(analysis_2$GradeAnswer) <- "Code Identification Score"
table1::label(analysis_2$GradeAnswerPct) <- "Code Identification Score (%)"
```

---

## 4. Define `Delta` as change in confidence score
```{r confidence scores}
#define delta
analysis_2$Delta <- analysis_2$PostConfidence - analysis_2$PreConfidence

#label variables
table1::label(analysis_2$PreConfidence) <- "Pre-Survey Confidence Score"
table1::label(analysis_2$PostConfidence) <- "Post-Survey Confidence Score"
table1::label(analysis_2$Delta) <- "Change in Confidence Score"
```

---

## 5. Drop remaining unnecessary columns
We'll make two dataframes. One with all of the variables, and one for the scoring / regression analysis.

For the scoring / regression analysis, this includes:

* percentcompleted
* ECE
* PLcodeswhy
* CodeexceptionsID
* TrainingOtherCat
* Trainingother

Also rename variables:

* ClinicalNon --> PositionType
* ECYN --> CodeProcedures
* PLcodes --> CodePreference
* GradeAnswer --> CodeScore
* GradeAnswerPct --> CodeScorePct


We'll also reorder the columns in a way that makes sense
```{r column cleaning}
#rename columns
analysis_3 <- analysis_2 %>%
                dplyr::rename(PositionType = ClinicalNon,
                              CodeProcedures = ECYN,
                              CodePreference = PLcodes,
                              CodeScore = GradeAnswer,
                              CodeScorePct = GradeAnswerPct)

#select columns to keep for scoring/regression analysis
analysis_4 <- analysis_3 %>%
                dplyr::select(c("FacilityLabel",
                                "PositionType",
                                "ShiftType",
                                "FacilityYears",
                                "HealthcareYears",
                                "FacilitiesNumber",
                                "CodeProcedures",
                                "Codeconfusion",
                                "Facilitiesdifferentcodes",
                                "CodePreference",
                                "Codeexceptions",
                                "TrainingOrientation",
                                "TrainingExercises",
                                "TrainingYearly",
                                "Traininglasttime",
                                "PreConfidence",
                                "PostConfidence",
                                "Delta",
                                "CodeScore",
                                "CodeScorePct"))
```

---

## 6. Save Processed Data
We can now save the combined dataset.
```{r save cleaned dataset}
#make a copy of last iteration in case other steps have to be added later
full_processed <- analysis_3

#location to save dataframe
analysis_processed_location <- here::here("data", "processed_data", "full_processed.rds")
analysis_processed_location2 <- here::here("data", "processed_data", "full_processed.xlsx")

#save data as RDS
saveRDS(full_processed, file = analysis_processed_location)

#export as Excel file
writexl::write_xlsx(full_processed, analysis_processed_location2)

#make a copy of last iteration in case other steps have to be added later
analysis_processed <- analysis_4

#location to save dataframe
analysis_processed_location3 <- here::here("data", "processed_data", "analysis_processed.rds")
analysis_processed_location4 <- here::here("data", "processed_data", "analysis_processed.xlsx")

#save data as RDS
saveRDS(analysis_processed, file = analysis_processed_location3)

#export as Excel file
writexl::write_xlsx(analysis_processed, analysis_processed_location4)
```